\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% Sections formatting
\titleformat{\section}
{\vspace{-4pt}\scshape\raggedright\large}
{}
{0em}
{}
[\color{black}\titlerule\vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
  \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{\(\circ\)}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/williamphetsinorath}{\Large William Phetsinorath}} &
  \href{mailto:contact@example.com}{contact@example.com}\\
  \href{https://linkedin.com/in/williamphetsinorath}{linkedin.com/in/williamphetsinorath} &
  \href{tel:+XXXXXXXXXXX}{+XX X XX XX XX XX} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart{}

\resumeSubheading{SFEIR}
{Neuilly-Sur-Seine, France}
{Data Architect}
{March 2022 - Present}
\resumeItemListStart{}
\resumeItem{
  Lead the architecture of the Big Data platform for several LVMH maisons,
  including the ingestion of multiple sales data sources from on-premises
  databases into BigQuery and then consumed by Microsoft Power BI.
}
\resumeItemListEnd{}

\resumeSubSubheading{Data Engineer}
{March 2021 - Present}
\resumeItemListStart{}
\resumeItem{
  Optimized satellite image computation time from hourly to minute scale for
  atmospheric anomaly detection on the Google Earth Engine to monitor and report
  the environmental impact of petrochemical infrastructures.
}
\resumeItem{
  Designed and implemented a complete data platform solution aggregating sales and
  supply chain data for a European hypermarket chain leveraging BigQuery, Apache
  Beam and Apache Airflow serviced by Tableau for use by industrial supply chain
  decision makers.
}
\resumeItem{
  Analyse data, extract key potential metrics and design Google Data Studio
  dashboards to optimise the management and detection of anomalies in the Leasys
  car fleet.
}
\resumeItemListEnd{}

\resumeSubSubheading{Software Engineer}
{October 2019 - March 2022}
\resumeItemListStart{}
\resumeItem{
  Developed the infrastructure certificate validator and secured IoT devices with
  PKI for the luxury smartwatch Louis Vuitton Tambour Horizon.
}
\resumeItem{
  Development and design of the authentication and payment infrastructure for the
  blockchain NFT marketplace of a French retailer of high-end sneakers on the
  Polygon network.
}
\resumeItem{
  Designed and implemented a complete IoT data processing platform for Birdz,
  including the tool chain and a non-technical domain-specific language for
  specifying the layout of frames, processing 200+ messages per second daily.
}
\resumeItemListEnd{}

\resumeSubSubheading{Research And Development Engineer}
{September 2018 - October 2019}
\resumeItemListStart{}
\resumeItem{
  Trained multiple enterprise on 1--3 days sessions on Google Cloud fundamentals
  and Google Infrastructure Kubernetes specialisation through the SFEIR Institute
  and Voxxed days.
}
\resumeItem{
  Promoted and advocated open source software development initiative,
  participating in internal and external conferences, events such as ngAir
  podcasts.
}
\resumeItem{
  Maintained and improved the transpiler architecture of the xLayers open source
  project. Allowing to generate Angular, Xamarin, Vue\ldots UI components from a
  SketchApp file format, streamlining the process between design and technical
  implementation.
}
\resumeItemListEnd{}

\resumeSubheading{École d'Alternance en Informatique}
{Ivry-sur-Seine, France}
{Teaching Assistant}
{September 2017 - October 2017}
\resumeItemListStart{}
\resumeItem{
  Organization of dynamic activities and workshops on the subjects studied as well
  as the evaluation interview at the end of the projects.
}
\resumeItem{
  Training in system languages: C, AWK, Perl; Bash; Web and Unix system
  fundamentals to +100 first year students.
}
\resumeItemListEnd{}

\resumeSubheading{KMB Labs}
{Paris, France}
{Software Engineer Intern}
{June 2017 - December 2017}
\resumeItemListStart{}
\resumeItem{
  Designed and implemented new conversation dialogue and user interactive element
  on Facebook Messenger chatbots, using React library and wit.ai Natural Language
  Processing service.
}
\resumeItem{
  Integrated a data ingestion pipeline processing 10,000+ customer jobs across
  multiple SQL, NoSQL and search engine databases daily on Amazon Web Service,
  delivering content to 1000+ active users daily.
}
\resumeItem{
  Introduced and integrated a methodology for collaborating with team members on
  trunk-based development using AWS CodeCommit to organize changes and Trello to
  assign tasks.
}
\resumeItemListEnd{}

\resumeSubHeadingListEnd{}


\section{Education}
\resumeSubHeadingListStart{}
\resumeSubheading{École d'Alternance en Informatique}
{Ivry-sur-Seine, France}
{Master of Network and Cyber Security Architect}
{September 2016 - October 2021}
\resumeSubHeadingListEnd{}


\section{Licenses \& Certifications}
\resumeSubHeadingListStart{}
\resumeSubheading{Professional Data Engineer Certification}
{Jun 2021 - Jun 2023}
{Certification}
{Google Cloud}
\resumeSubheading{Professional Machine Learning Engineer Certification}
{Jun 2021 - Jun 2023}
{Certification}
{Google Cloud}
\resumeSubheading{Certified Kubernetes Application Developer}
{Febuary 2021 - Febuary 2024}
{Certification}
{Linux Foundation}
\resumeSubheading{Terraform Associate}
{January 2021 - January 2023}
{Certification}
{HashiCorp}
\resumeSubheading{Professional Cloud Developer Certification}
{May 2019 - April 2023}
{Certification}
{Google Cloud}
\resumeSubHeadingListEnd{}

\section{Technical Skills \& Interests}
\resumeSubHeadingListStart{}
\resumeItem{
  \textbf{Languages:}{
    OCaml, Erlang/Elixir, Rust, Go, C/C++, SQL, Python, JavaScript/TypeScript
  }
}
\resumeItem{
  \textbf{Technologies:}{
    Tensorflow, Kubernetes, Apache Beam, Game Server Development, Blockchain
  }
}
\resumeSubHeadingListEnd{}

\end{document}
