% !TEX program = xelatex
% !TeX encoding = UTF-8

\documentclass[letterpaper,11pt]{article}

% Remove margins
\usepackage[empty]{fullpage}

% Customize section titles
\usepackage{titlesec}

% Customize lists
\usepackage{enumitem}

% Add links to URLs
\usepackage[hidelinks]{hyperref}

% Make tables more flexible
\usepackage{tabularx}

% Multi-language support
\usepackage[bidi=default]{babel}

% Font support
\usepackage{fontspec}
\usepackage{microtype}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% Use the same font for URLs
\urlstyle{same}

% Remove extra space of the page
\raggedbottom{}
\raggedright{}

% Remove extra space between columns
\setlength{\tabcolsep}{0in}

% Remove extra space between footer and text
\setlength{\footskip}{5pt}

% Sections formatting
\titleformat{\section}
{\vspace{-4pt}\scshape\raggedright\large}
{}
{0em}
{}
[\titlerule\vspace{-5pt}]

% Change bullet points to circles
\renewcommand{\labelitemii}{\(\circ\)}

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\Large William Phetsinorath} &
	\href{mailto:contact@shikanime.studio}{contact@shikanime.studio}\\
	\href{https://links.shikanime.studio}{links.shikanime.studio} &
	% Where it all began, where it'll end.
	% From a little dream, to a big dream.
	\href{tel:+XXXXXXXXXXX}{+XX X XX XX XX XX} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart{}

\resumeSubheading{SFEIR}
{Since February 2021}
{Solutions Architect}
\resumeItemListStart{}
\resumeItem{
	Design and implementation of highly scalable MLOps and data platforms for
	organizations of varying sizes, by integrating diverse on-premise and
	cloud-based data sources.
}
\resumeItem{
	Responsible for designing and implementing data architecture solutions using
	various technologies such as Google Cloud, Amazon Web Services, Apache Beam,
	DBT and BigQuery.
}
\resumeItem{
	Provide technical leadership to a team of data engineers and data scientists,
	driving innovation and identifying opportunities for process optimization and
	automation.
}
\resumeItemListEnd{}


\resumeSubSubheading{Cloud Engineer}
{September 2018 - October 2021}
\resumeItemListStart{}
\resumeItem{
	Provided expert guidance on cloud transformation for multiple companies,
	driving successful adoption of cloud-native technologies, including serverless
	and Kubernetes.
}
\resumeItem{
	Architected scalable and resilient cloud solutions, incorporating DevOps best
	practices to ensure high availability, performance, and security.
}
\resumeItemListEnd{}


\resumeSubheading{Orano}
{Since November 2023}
{Machine Learning Consultant}
\resumeItemListStart{}
\resumeItem{Undisclosed.}
\resumeItemListEnd{}


\resumeSubheading{Webedia}
{Since September 2023}
{Cloud Engineer Contractor}
\resumeItemListStart{}
\resumeItem{Undisclosed.}
\resumeItemListEnd{}


\resumeSubheading{TotalEnergies}
{Since July 2021}
{Data Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Industrialization of satellite image analysis research, working closely
	with a team of data scientists to develop statistical models and deep learning
	algorithms on the Google Earth Engine. Resulted in successful monitoring and
	reporting of crop health, solar panel yields, environmental impacts, and
	natural disaster damage detection.
}
\resumeItemListEnd{}


\resumeSubheading{TAG Heuer}
{June 2023 - November 2023}
{Cloud Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	I spearhead the management and optimization of the division's cloud
	infrastructure, encompassing network architecture, access control, system
	integration, and all organizational cloud platform security-related matters.
}
\resumeItemListEnd{}


\resumeSubheading{Renault-Nissan-Mitsubishi}
{September 2022 - Jun 2023}
{Cloud Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed and deployed a mission-critical IoT gateway on Kubernetes, utilizing
	Canary deployment strategy and end-to-end encryption to route traffic for over
	three million smart cars globally.
}
\resumeItemListEnd{}


\resumeSubheading{Paprec}
{January 2023 - April 2023}
{Machine Learning Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed and implemented a Kubeflow-based MLOps pipeline on Vertex AI to enable
	end-to-end machine learning workflows, leveraging PyTorch for model training and
	deployment.
}
\resumeItemListEnd{}


\resumeSubheading{Amadeus}
{January 2023 - February 2023}
{Machine Learning Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Developed and deployed a robust MLOps pipeline on Vertex AI using Kubeflow to
	enable end-to-end machine learning workflows. Employed Tensorflow and Tensorflow
	Extended for model training, evaluation, deployment, and monitoring of skew and
	drift. Resulted in enhanced model experimentation, improved efficiency and
	move-to-production time.
}
\resumeItemListEnd{}


\resumeSubheading{Birdz}
{October 2019 - November 2022}
{Cloud Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed and deployed a high-throughput streaming and batch data pipeline
	infrastructure capable of handling over 2,000 messages per second, while ensuring
	fault-tolerant traffic management for optimal data flow and reliability.
}
\resumeItem{
	Implemented performance monitoring in all components using Open Telemetry,
	consumed through Stackdriver, Error Reporting, and Cloud Tracing to ensure
	continuous optimization of the data pipeline's performance and efficiency.
}
\resumeItem{
	Participated in the design of a Domain-Specific Language (DSL), which included the
	declarative binary frame reader, flow control, and Input/Output (IO) interface
	for efficient and streamlined data processing.
}
\resumeItem{
	Designed and implemented a lightweight JSON-RPC-based protocol around the
	OCaml language runtime to facilitate microservices development through HTTP,
	browser via a Web worker, and Command-Line Interface (CLI), resulting in a more
	efficient and scalable microservices environment.
}
\resumeItemListEnd{}


\resumeSubheading{LVMH}
{February 2022 - October 2022}
{Data Architect Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed and implemented an effective ingestion architecture to handle complex
	data sources, ensuring daily data freshness.
}
\resumeItem{
	Developed an extensible and flexible Terraform module that can be customized for
	different sub-brands of the group, increasing data platform reusability and
	coherence.
}
\resumeItem{
	Provided technical guidance to developers on selecting appropriate input formats,
	including Avro, Parquet, and CSV, and evaluated their constraints for over 250
	tables, including non-english UTF-8 text encoding.
}
\resumeItemListEnd{}


\resumeSubheading{Leasys Rent}
{May 2022 - July 2022}
{Cloud Architect Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed and implemented a modern application architecture solution for Leasys Rent,
	leveraging Lift and Shift to OpenID authentication. Successfully integrated the
	new system without causing disruptions to the existing system.
}
\resumeItemListEnd{}


\resumeSubSubheading{Data Engineer Contractor}
{February 2021 - June 2021}
\resumeItemListStart{}
\resumeItem{
	Analyzed and extracted relevant metrics for customer needs using SQL on
	BigQuery, leading to improved data-driven insights for business decisions.
}
\resumeItem{
	Created interactive and user-friendly Google Data Studio dashboards for daily
	monitoring of accounting metrics, vehicle fleet status, and invoice tracking,
	resulting in improved operational efficiency and timely detection of fleet
	anomalies.
}
\resumeItemListEnd{}


\resumeSubheading{Futures Factory}
{January 2022 - March 2022}
{Cloud Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed and developed a secure user authentication system supporting Metamask
	and Magic.link, with an asymmetric cryptographic challenge for enhanced
	security.
}
\resumeItem{
	Improved the user experience by implementing ERC2771 on smart contracts,
	enabling the transfer of NFTs without gas fees.
}
\resumeItem{
	Integrated Stripe fiat payment system with the service submitting ERC2771
	transactions to the Polygon blockchain.
}
\resumeItem{
	Designed a state machine to orchestrate fiat and on-chain transactions, resolved
	issues such as front-running bots, currency conversion, and ensured optimal user
	experience during the purchasing process.
}
\resumeItemListEnd{}


\resumeSubheading{The Estée Lauder Companies Inc.}
{September 2021 - January 2022}
{Data Architect Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed a Lift and Shift migration plan and assisted the customer in automating
	and optimizing an MVP through the use of Python scripts, eliminating manual
	processes and improving operational efficiency.
}
\resumeItem{
	Provided technical and architectural guidance to the development team, ensuring
	compatibility with legacy systems and improving overall system performance.
}
\resumeItemListEnd{}


\resumeSubheading{GALEC - Groupement d'Achats E.LECLERC}
{August 2021 - January 2022}
{Data Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Designed and implemented a scalable data ingestion architecture to support over
	15,000 point-of-sale sales per day on a European scale, utilizing Apache Beam
	for data normalization and BigQuery for data warehousing.
}
\resumeItem{
	Processed and analyzed 2.5 terabytes of data daily on Cloud Dataflow and
	BigQuery, improving data-driven insights for supply chain operational decisions
	and providing stakeholders with up-to-date information.
}
\resumeItem{
	Automated daily, weekly, and monthly task workflows using Apache Airflow,
	improving the overall efficiency and productivity of the data platform and
	enabling for more impactful data analysis tasks.
}
\resumeItemListEnd{}


\resumeSubheading{Evidian - Atos Cyber Security}
{December 2020 - March 2021}
{Cloud Engineer Contractor}
\resumeItemListStart{}
\resumeItem{
	Integrated Evidian IDaaS software into Google Cloud Marketplace, developing
	event-driven integrations with internal Google Marketplace infrastructure.
	Created backend API for subscription creation, consumption monitoring, customer
	registration, and Evidian backoffice integration, boosting service delivery
	capabilities.
}
\resumeItemListEnd{}


\resumeSubheading{KMB Labs}
{June 2017 - December 2017}
{Software Engineer Intern}
\resumeItemListStart{}
\resumeItem{
	Developed and implemented new conversational dialogues and user interactive
	elements for Facebook Messenger chatbots using React library and wit.ai Natural
	Language Processing service, enhancing the chatbot's user experience and
	engagement.
}
\resumeItem{
	Implemented a scalable data ingestion pipeline to process 10,000+ customer jobs
	across multiple SQL, NoSQL and search engine databases daily on Amazon Web
	Service, providing content to 10000+ active users daily, and enhancing the
	chatbot's functionalities.
}
\resumeItemListEnd{}


\resumeSubheading{École d'Alternance en Informatique}
{September 2017 - October 2017}
{Teaching Assistant}
\resumeItemListStart{}
\resumeItem{
	Designed and facilitated dynamic activities and workshops to engage +100 first
	year students in learning system languages such as C, AWK, Perl, Bash, Web, and
	Unix system fundamentals.
}
\resumeItem{
	Conducted evaluation interviews at the end of student projects, providing
	constructive feedback and guidance for improvement.
}
\resumeItemListEnd{}
\resumeSubHeadingListEnd{}


\section{Education}
\resumeSubHeadingListStart{}
\resumeSubheading{École d'Alternance en Informatique}
{2017 - 2021}
{Master of Network and Cyber Security Architect}
\resumeSubHeadingListEnd{}


\section{Certifications}
\resumeSubHeadingListStart{}
\resumeSubheading{TensorFlow Developer Certification}
{2022}
{Google}
\resumeSubheading{Professional Data Engineer}
{2021}
{Google}
\resumeSubheading{Professional Machine Learning Engineer}
{2021}
{Google}
\resumeSubheading{Certified Kubernetes Application Developer}
{2021}
{Linux Foundation}
\resumeSubheading{Terraform Associate}
{2021}
{HashiCorp}
\resumeSubheading{Professional Cloud Developer}
{2019}
{Google}
\resumeSubHeadingListEnd{}


\section{Languages}
\resumeSubHeadingListStart{}
\resumeItem{
	\textbf{French:}{
		Native or bilingual proficiency
	}
}
\resumeItem{
	\textbf{English:}{
		Native or bilingual proficiency
	}
}
\resumeItem{
	\textbf{Mandarin Chinese:}{
		Limited working proficiency
	}
}
\resumeItem{
	\textbf{Japanese:}{
		Elementary proficiency
	}
}
\resumeSubHeadingListEnd{}


\section{Technical Skills \& Interests}
\resumeSubHeadingListStart{}
\resumeItem{
	\textbf{Languages:}{
		Go, C/C++, SQL, Python, OCaml
	}
}
\resumeItem{
	\textbf{Technologies:}{
		TensorFlow, PyTorch, Apache Beam, Kubernetes, BigQuery
	}
}
\resumeSubHeadingListEnd{}

\end{document}
